---
title: "Cryptocurrencies"
author: "Kenneth Osborne"
date: '`r Sys.Date()`'
output:
  html_document:
    number_sections: true
    fig_caption: true
    toc: true
    fig_width: 7
    fig_height: 4.5
    theme: cosmo
    highlight: tango
    code_folding: hide

---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo=TRUE)
knitr::opts_chunk$set(cache=TRUE)
myWD='C:/Users/Duckie/Documents/myR/cryptocurrencies/'
knitr::opts_chunk$set(root.dir = myWD)
```

# Introduction

Here we review the relative value of Bitcoin (BTC) to Litecoin(LTC).

## Load libraries and helper functions

```{r, message = FALSE}
library('tidyverse') # all around good package
library('data.table') # data manipulation
library('lubridate') # date and time
library('corrplot') # visualization
library('caret') # modelling
```

## Load data



```{r warning=FALSE, results=FALSE}
setwd('cryptocurrencypricehistory')

filenames <- list.files(pattern="*.csv")
myfiles   <- lapply(filenames, read.csv)

```

put names on things

```{r}
filenames <- sapply(filenames, function(x) {
    gsub("_price.csv", "", x)
    
})

coindata <- list

for (i in 1:length(myfiles)) {
    coindata[[i]]<- myfiles[[i]][,1:2] %>% 
        cbind( 
            Coin =
                rep(filenames[i],nrow(myfiles[[i]]))
        )
}

```

# Data exploration

Here we see what our data look like for the first time.

```{r}
# bitcoin
# litecoin
```
We're just interested in the daily average for now. We then combine the two sets

```{r}
btc <- bitcoin  %>% select(Date,Average) %>% 
    transmute(Date=Date,
              BTC=Average)
ltc<- litecoin %>% select(Date,Average) %>%
    transmute(Date=Date,
              LTC=Average)
df<- inner_join(btc, ltc, by = "Date")
df<- df[complete.cases(df),]
# df
```
We can try to compare how bitcoin is changing vs time for both bitcoin and litecoin, but they're on such different scales that we have to use a logarithmic scale to see all resolutions clearly. To do that we need to put everything in long format.

```{r}
avg <- df %>% select(Date,BTC,LTC)
avg.long <- melt(avg, id="Date")

ggplot(avg.long, aes(x=Date,y=value,color=variable)) + 
    scale_y_log10() +
    geom_line() + 
    theme_light()
```

It often looks like bitcoin and litecoin are moving in tandem, but does one yield better returns than the other?

To answer this question, we'll try to rescale the problem.

```{r}
df<- df %>% mutate(BTCpct= BTC/(df$BTC %>% tail(1))-1, LTCpct= LTC/(df$LTC %>% tail(1))-1)
# df
```



```{r}
pct <- df %>% select(Date,BTCpct,LTCpct)
pct.long <- melt(pct, id="Date")

ggplot(pct.long, aes(x=Date,y=value,color=variable)) + 
    geom_line() + 
    theme_light()
```