---
title: "Cryptocurrencies"
author: "Kenneth Osborne"
date: '`r Sys.Date()`'
output:
  html_document:
    number_sections: true
    fig_caption: true
    toc: true
    fig_width: 7
    fig_height: 4.5
    theme: cosmo
    highlight: tango
    code_folding: hide

---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo=TRUE)
knitr::opts_chunk$set(cache=TRUE)
myWD='C:/Users/Duckie/Documents/myR/cryptocurrencies/'
knitr::opts_chunk$set(root.dir = myWD)
```

# Introduction

Here we review the relative value of Bitcoin (BTC) to Litecoin(LTC).

## Load libraries and helper functions

```{r, message = FALSE}
library('tidyverse') # all around good package
library('data.table') # data manipulation
library('lubridate') # date and time
library('corrplot') # visualization
library('caret') # modelling
```

## Load data



```{r warning=FALSE, results=FALSE}
setwd('cryptocurrencypricehistory')

filenames <- list.files(pattern="*.csv") 
myfiles   <- lapply(filenames, read.csv)

```

put names on things

```{r}
filenames <- sapply(filenames, function(x) {
    gsub("_price.csv", "", x)
    
})%>% unname

for (i in 1:length(myfiles)) {
    myfiles[[i]]<- myfiles[[i]] %>% 
        select(1:2) %>% 
        cbind(Coin = 
                  rep(filenames[i],
                      nrow(myfiles[[i]]))
              )
}

df <- do.call("rbind",myfiles) %>% mutate(Date=mdy(Date))

```

# Data exploration

Here we see what our data look like for the first time.

```{r}
# bitcoin
# litecoin
```
We're just interested in the daily average for now. We then combine the two sets

```{r}

```
We can try to compare how bitcoin is changing vs time for both bitcoin and litecoin, but they're on such different scales that we have to use a logarithmic scale to see all resolutions clearly. To do that we need to put everything in long format.

```{r}
ggplot(df, aes(x=Date,y=Open,color=Coin)) + 
    scale_y_log10() +
    geom_line() + 
    theme_light()
```

It often looks like bitcoin and litecoin are moving in tandem, but does one yield better returns than the other?

To answer this question, we'll try to rescale the problem.

```{r}
mydate <- "2017-06-01"
prices <- df %>% filter(Date==mydate) %>% transmute(Coin=Coin, Pct = Open)
```



```{r}
pct_df <- left_join(df,prices)
pct_df <- mutate(pct_df,Pct = Open/Pct-1)

ggplot(pct_df, aes(x=Date,y=Pct,color=Coin)) + 
    # scale_y_log10() +
    geom_line() + 
    theme_light()
```