---
title: "Cryptocurrencies"
author: "Kenneth Osborne"
date: '`r Sys.Date()`'
output:
  html_document:
    number_sections: true
    fig_caption: true
    toc: true
    fig_width: 7
    fig_height: 4.5
    theme: cosmo
    highlight: tango
    code_folding: hide

---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo=TRUE)
knitr::opts_chunk$set(cache=TRUE)
myWD='C:/Users/Duckie/Documents/myR/cryptocurrencies/'
knitr::opts_chunk$set(root.dir = myWD)
```

# Introduction

Here we review the relative value of Bitcoin (BTC) to Litecoin(LTC).

## Load libraries and helper functions

```{r, message = FALSE}
library('tidyverse') # all around good package
library('data.table') # data manipulation
library('forcats') # factor manipulation
library('lubridate') # date and time
library('Quandl')
library('corrplot') # visualization
library('caret') # modelling
```

## Load data

We use data from Quandl to get the daily prices of both BTC and LTC.

```{r warning=FALSE, results=FALSE}
bitcoin  <- Quandl("BTCE/USDBTC",collapse = "daily") %>% as.tbl()
litecoin <- Quandl("BTCE/USDLTC",collapse = "daily") %>% as.tbl()
```

# Data exploration

Here we see what our data look like for the first time.

```{r}
bitcoin
litecoin
```
We're just interested in the daily average for now. We then combine the two sets

```{r}
btc <- bitcoin  %>% select(Date,Average,Volume,`Volume (Currency)`) %>% 
    transmute(Date=Date,
              BTC=Average,
              BTC.vol.usd=Volume,
              BTC.vol=`Volume (Currency)`)
ltc<- litecoin %>% select(Date,Average,Volume,`Volume (Currency)`) %>%
    transmute(Date=Date,
              LTC=Average,
              LTC.vol.usd=Volume,
              LTC.vol=`Volume (Currency)`)
df<- inner_join(btc, ltc, by = "Date")
df<- df[complete.cases(df),] %>% mutate(LTCvsBTC= LTC/BTC)
df
```
We can try to compare how bitcoin is changing vs time for both bitcoin and litecoin, but they're on such different scales that we have to use a logarithmic scale to see all resolutions clearly. To do that we need to put everything in long format.

```{r}
avg <- df %>% select(Date,BTC,LTC,LTCvsBTC)
avg.long <- melt(avg %>% select(-LTCvsBTC),
                 id="Date")

ggplot(avg.long, aes(x=Date,y=value,color=variable)) + 
    scale_y_log10() +
    geom_line() + 
    theme_light()
```

It often looks like 

Alternatively, we can see the relative fluctuation of LTC with respect to the BTC. This is a sensible solution, especially because many platforms only let you trade cryptocurrencies against one another.

```{r}
ggplot(avg,aes(Date,LTCvsBTC)) + 
    geom_line(col=2,alpha=.5) + 
    theme_light() +
    theme(legend.position = "none")
```

